Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-06 paper/paper.tex
added three sentences at end of results to point out lack of evidence for summation of genetic defects;

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild type.
The other three point mutants (PB1-G206S, PB1-K279R, and NS2-E47G) did not increase IFN induction---an unsurprising finding, since we also expect some mutations without an IFN-enhancing effect to be found in IFN+ cells by chance.
But overall, the results in \FIG{validation} validate that the viral defects in single IFN+ cells often cause increased IFN production.

>>>>

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild type.
The other three point mutants (PB1-G206S, PB1-K279R, and NS2-E47G) did not increase IFN induction---an unsurprising finding, since we also expect some mutations without an IFN-enhancing effect to be found in IFN+ cells by chance.
But overall, the results in \FIG{validation} validate that the viral defects in single IFN+ cells often cause increased IFN production.
Curiously, none of the mutations tested induce interferon deterministically (ie in all infected cells), indicating additional heterogeneity in response driven by unsampled heterogeneity in viral samples or host signaling pathways.
Due to our single-cell approach, we can determine that it is unlikely that this heterogeneity is simply a summation of those immunostimulatory genetic features described here, as neither of the immunostimulatory PB1 mutations were identified in interferon-producing infections lacking the NS gene segment or possessing an internally-deleted segment, two of the NS null infections found in interferon positive cells wherein infection was  otherwise entirely wild-type in sequence, and the PB1 deletion was found in an infection that was wild-type other than a mutation in NA, unlikely to have precipitated interferon induction.
Therefore there remains considerable heterogeneity in interferon induction beyond those genetic features identified here.
